### 2021-11-05 manuscript.Rmd
Changed subscripts in the Bayes plots (fig 2a and 2b)

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
---

@@

## *Group-sequential procedures* 
The most common procedure for sequential hypothesis testing is a group-sequential (GS) design [@proschan2006; @schonbrodt2017]. The goal of GS procedures is to efficiently reject a null hypothesis in favor of an alternative hypothesis. In a prototypical group-sequential procedure [e.g., the Pocock correction or the O'Brien-Fleming correction\; @fleming1984; @pocock1977], a researcher is allowed to look at the data several times during the course of a study.

@@

The SBF procedure has several properties of interest. First, it is symmetric: it allows researchers to examine whether the obtained data is better predicted by, for example, $H_+$ than $H_0$, or vice versa. Second, it is highly flexible: it allows researchers to take as many looks at incoming data as desired [even after every study participant; @schonbrodt2017]. Third, it does not allow type I and type II error rates to be defined a priori [although simulations can be run to choose an optimal design that controls expected error rates, @schonbrodt2018; @schonbrodt2017; @stefan2020]. Fourth, it allows (and requires) researchers to express their uncertainty about the expected effect size by means of a prior distribution.

@@

To reflect the expectation of a "medium" effect size, the researcher can, for example, choose the default prior distribution [i.e., a Cauchy distribution with scale parameter *r* = $\sqrt2/2$; @morey2011; @schnuerch2020; @schonbrodt2017]. In addition, the researcher could (for example, on the basis of simulations) choose $BF_{+0}$ = 3 as a decision threshold [commonly referred to as "*moderate evidence*"; @schonbrodt2017]. This decision threshold _t_* implies that the researcher is content to stop sampling once the data is 3 times more likely under $H_+$ than under $H_0$, or vice versa. Figure 2A (2B) provides a visual example of a situation in which the Bayes Factor indicates that the data is 3 times more likely under $H_+$ ($H_0$).

@@

Second, the ISP only applies to research contexts in which a single, key hypothesis is tested [@miller2020]. This, unfortunately, is unusually restrictive to the settings in which sequential hypothesis testing is common. For example, medical trials often have multiple "*endpoints*" that need to be monitored at the same time: a primary endpoint (e.g., treatment success or survival) and multiple secondary -- but exceedingly important -- efficacy or safety endpoints [@wassmer2016]. An enlightening example can be found in the FDA approval process for carvedilol (a drug developed for congestive heart failure), in which the endpoints were -- among other things -- mortality, distance that can be walked on a treadmill, exercise tolerance, cardiovascular hospitalizations, quality of life, and the patient and physician's global assessment [@fisher1999; @fisher1999a].

@@

To some, the use of tail areas in hypothesis testing is an admirable feature that ensures long-run error control; to others, it is a bug that defies our ability to articulate the evidence for competing hypotheses provided by the experiment at hand. Controlling (long-run) error rates and quantifying (short-run) evidential strength are both worthy scientific goals. However, you can't have one without implicitly abstaining from the other [unless you follow the Likelihood paradigm of statistical inference, which is beyond the scope of this paper; @blume2002; @goodman1988; @schnuerch2020]. Ultimately, the question is what is more important to the researcher [@lakens2020a]: controlling long-run error rates or quantifying short-run evidential strength [@dienes2011].

@@

Conventionally, the Null-Hypothesis Significance test is not able to distinguish between failures to reject the null hypothesis due to evidence of absence (a True Negative result) or absence of evidence (an Inconclusive result). Therefore, we labeled all failures to reject the null on the basis of a fixed-sample hypothesis test as Inconclusive. It will be noted, however, that it is possible to overcome this limitation of conventional practice by testing against range predictions rather than a nil-null hypothesis. Instead of testing the nil-null hypothesis that the effect is exactly zero, researchers can test whether effects more extreme than a range of predicted or practically important effect sizes can be rejected -- for example, by virtue of an equivalence test or a minimum-effect test [@lakens2018; @lakens2020a].

@@

## Figure 2A
## *Bayes Favor in Favor of the Alternative Hypothesis* 
\noindent
```{r, fig.heigth = 10, fig.width = 4.5}
knitr::include_graphics("figures/figure2a.tiff", dpi = 1200)
```

>>>>

documentclass     : "apa7"
classoption       : "man"
output            : papaja::apa6_word
---

@@

## *Group-sequential procedures* 
The most common procedure for sequential hypothesis testing is a group-sequential (GS) design [@proschan2006; @schonbrodt2017]. The goal of GS procedures is to efficiently reject a null hypothesis in favor of an alternative hypothesis. In a prototypical group-sequential procedure [e.g., the Pocock correction or the O'Brien-Fleming correction, @fleming1984; @pocock1977], a researcher is allowed to look at the data several times during the course of a study.

@@

The SBF procedure has several properties of interest. First, it is symmetric: it allows researchers to examine whether the obtained data is better predicted by, for example, $H_+$ than $H_0$, or vice versa. Second, it is highly flexible: it allows researchers to take as many looks at incoming data as desired [even after every study participant\; @schonbrodt2017]. Third, it does not allow type I and type II error rates to be defined a priori [although simulations can be run to choose an optimal design that controls expected error rates, @schonbrodt2018; @schonbrodt2017; @stefan2020]. Fourth, it allows (and requires) researchers to express their uncertainty about the expected effect size by means of a prior distribution.

@@

To reflect the expectation of a "medium" effect size, the researcher can, for example, choose the default prior distribution [i.e., a Cauchy distribution with scale parameter *r* = $\sqrt2/2$\; @morey2011; @schnuerch2020; @schonbrodt2017]. In addition, the researcher could (for example, on the basis of simulations) choose $BF_{+0}$ = 3 as a decision threshold [commonly referred to as "*moderate evidence*"\; @schonbrodt2017]. This decision threshold _t_* implies that the researcher is content to stop sampling once the data is 3 times more likely under $H_+$ than under $H_0$, or vice versa. Figure 2A (2B) provides a visual example of a situation in which the Bayes Factor indicates that the data is 3 times more likely under $H_+$ ($H_0$).

@@

Second, the ISP only applies to research contexts in which a single, key hypothesis is tested [@miller2020]. This, unfortunately, is unusually restrictive to the settings in which sequential hypothesis testing is common. For example, medical trials often have multiple "*endpoints*" that need to be monitored at the same time: a primary endpoint (e.g., treatment success or survival) and multiple secondary -- but exceedingly important -- efficacy or safety endpoints [@wassmer2016]. An enlightening example can be found in the FDA approval process for carvedilol (a drug developed for congestive heart failure), in which the endpoints were -- among other things -- mortality, distance that can be walked on a treadmill, exercise tolerance, cardiovascular hospitalizations, quality of life, and the patient and physician's global assessment [@fisher1999].

@@

To some, the use of tail areas in hypothesis testing is an admirable feature that ensures long-run error control; to others, it is a bug that defies our ability to articulate the evidence for competing hypotheses provided by the experiment at hand. Controlling (long-run) error rates and quantifying (short-run) evidential strength are both worthy scientific goals. However, you can't have one without implicitly abstaining from the other [unless you follow the Likelihood paradigm of statistical inference, which is beyond the scope of this paper\; @blume2002; @goodman1988; @schnuerch2020]. Ultimately, the question is what is more important to the researcher [@lakens2021]: controlling long-run error rates or quantifying short-run evidential strength [@dienes2011].

@@

Conventionally, the Null-Hypothesis Significance test is not able to distinguish between failures to reject the null hypothesis due to evidence of absence (a True Negative result) or absence of evidence (an Inconclusive result). Therefore, we labeled all failures to reject the null on the basis of a fixed-sample hypothesis test as Inconclusive. It will be noted, however, that it is possible to overcome this limitation of conventional practice by testing against range predictions rather than a nil-null hypothesis. Instead of testing the nil-null hypothesis that the effect is exactly zero, researchers can test whether effects more extreme than a range of predicted or practically important effect sizes can be rejected -- for example, by virtue of an equivalence test or a minimum-effect test [@lakens2018; @lakens2021].

@@

## Figure 2A
## *Bayes Factor in Favor of the Alternative Hypothesis* 
\noindent
```{r, fig.heigth = 10, fig.width = 4.5}
knitr::include_graphics("figures/figure2a.tiff", dpi = 1200)
```
